---
title: "Stock Orders"
author: "Lela Sengupta"
format: html
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: false
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
#| label: data_load
#| message: false
#| warning: false


x <- read_csv("q1_2024_all.csv") |> 
  janitor::clean_names() |>
#grouped numbers into character categories based on range of volatility ranks and mcap ranks
   mutate(volatility_rank = 
            case_when(volatility_rank %in% c(1,4) ~ "low",
                      volatility_rank %in% c(5,7) ~ "mid" ,
                      volatility_rank %in% c(8,10) ~ "high"),
    mcap_rank = case_when(mcap_rank %in% c(1, 4) ~ "low",
                         mcap_rank %in% c(5, 7) ~ "mid",
                         mcap_rank %in% c(8, 10) ~ "high"),
  #log transformed data to make it fit a normal distribution
    log_hidden = log(hidden)) |>
  select(security, ticker, volatility_rank, hidden, date, log_hidden, mcap_rank) |>
#selected specific date, removed negative values, removed ETFs
  filter(hidden > 0, security == "Stock") |> drop_na()
#removed NaNs
stock <- na.omit(x)
#randomly selected stocks
stock <- stock %>% sample_n(10000)



```


```{r}
#| label: model
#| cache: true

fit_sec8 <- brm(formula = log_hidden ~ volatility_rank + mcap_rank,
    data = stock,
    family = gaussian(),
    silent = 2,
    refresh = 0,
    seed = 9)
```

```{r}
#| label: plot
fit_sec8 |>
  add_epred_draws(newdata = tibble(volatility_rank = c("low", "mid", "high"), mcap_rank = c("low", "mid", "high"))) |>
  ggplot(aes(x = mcap_rank, y = .epred, fill = volatility_rank)) + 
  geom_violin(alpha = 0.5) + 
  scale_y_continuous(limits = c(3, 9)) +
  theme_classic() +
  labs(title = "Hidden Orders (log) per Stock Type",
       subtitle = "Stocks with high volatility and high market capitalizations experience the most hidden orders",
       x = "Market Capitalization",
       y = "Hidden Orders (log)",
       fill = "Volatility Rank")
```
## Analysis
Using early 2024 data from the United States Securities and Exchange Commission (SEC), I seek to understand the relationship between a stock's volatility level and hidden orders in US markets within the next ten years. There is some concern that the SEC's methods of measuring volatility may slightly differ from individual investors. I created a Bayesian linear regression model with the logarithmic transformation of hidden orders as the dependent variable, and volatility rank and market capitalization as independent variables. Low volatility stocks experience about a 54% decrease in hidden orders compared to high volatility stocks, although that number could be as high as 63% and as low as 43%. These results could also vary with stock's market capitalization. 


## Stock Info
**Volatility**: define here, includes methods of quantifying it

**Hidden Orders**: define here

**Market Capitalization**: define here


- model 8: log transformed ver with mcap_rank
